### 2021-03-04 ch02_scientific_background/scientific_background.tex
Restructured thesis and removed unnecessary parts
Added list of figures and list of tables

%=============================================================================%
%                                Dissertation                                 %
%                               Manuel Schlund                                %
%                                  (c) 2020                                   %
%=============================================================================%
%                            Scientific Background                            %
%=============================================================================%

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/esms_historical_evolution.pdf}
  \caption{Historical evolution of coupled climate models over the last 45
    years. In early days, these models were so-called \acfp{AOGCM}, which only
    included three components: the atmosphere, the land surface and the ocean.
    Over the time, the individual components grew in complexity and included a
    wider range of processes (illustrated by the growing cylinders).
    Eventually, more and more components (aerosols, carbon cycle, \etc{}) were
    added to the coupled system, forming the modern \acfp{ESM}.
    \IPCCReproducedFrom{Cubasch2013}{their figure 1.13}.}
  \label{fig:02:esms_historical_evolution}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/cmip6.pdf}
  \caption{Schematic of the experiment design of Phase 6 of the \acl{CMIP}
    (\acs{CMIP}6). The center of the circle illustrates the four \acs{DECK}
    (\acl{DECK}) experiments and the \acs{CMIP}6 historical simulation. The
    circular sectors show additional science themes that can be explored
    through the 21 \acs{CMIP}6-Endorsed \acfp{MIP}.
    \SpringerAdaptedFrom{Simpkins2017}.}
  \label{fig:02:cmip6}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/sources_of_uncertainty.pdf}
  \caption{Schematic illustrating the importance of different sources of
    uncertainties in climate model projections and their evolution in time. (a)
    Time series of the anomaly of the decadal and global mean surface
    temperature relative to the period \range{1961}{1980}. The black line
    shows the historical observations with estimates of uncertainty from
    climate models (gray). The remaining colors show different sources of
    uncertainty in future climate projections: Natural variability (orange),
    climate response uncertainty (blue) and emission uncertainty (green)
    \autocite{Hawkins2009, Hawkins2010}. Climate response uncertainty can
    increase (b) in newer generations of climate models when a new process is
    discovered to be relevant or decrease (c) with additional model
    improvements and observational constraints.
    \IPCCReproducedFrom{Cubasch2013}{their FAQ 1.1, figure 1}.}
  \label{fig:02:sources_of_uncertainty}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/feedbacks_overview.pdf}
  \caption{Climate feedbacks and corresponding time scales. \enquote{+} refers
    to positive feedbacks, which amplify the effect of the external forcing
    (\eg{} the water vapor feedback). \enquote{-} refers to negative feedbacks,
    which diminish the effect of the external forcing (\eg{} the longwave
    radiation feedback). \enquote{+/-} refers to feedbacks which might be
    either positive or negative (\eg{} the cloud feedback). The smaller box
    highlights the large differences in time scales for the various feedbacks.
    \IPCCReproducedFrom{Cubasch2013}{their figure 1.2}.}
  \label{fig:02:feedbacks_overview}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/gregory_regression.pdf}
  \caption{Global and annual mean net \acf{TOA} radiation $N$ versus the change
    in global and annual mean \acl{T} $\Delta T$ for 150 years of a simulation
    with an abrupt quadrupling of the atmospheric \acs{CO2} concentration
    (\nxcotwo{4}) for the \acs{CMIP}5 \acl{MMM} (blue circles). To account for
    energy leakage and model drift, a linear fit of the corresponding
    pre-industrial control run is subtracted from the \nxcotwo{4} simulation.
    As given by \cref{eq:02:N_vs_delta_t}, the slope of the linear regression
    (black line) corresponds to the climate feedback parameter $\lambda$, and
    the \yintercept{} corresponds to the radiative forcing $F_\mathtxt{4x}$.
    These can be used to calculate the \acf{ECS} with the Gregory regression
    method according to \cref{eq:02:ecs} \autocite{Gregory2004}. \acs{ECS} is
    equivalently given by the \xintercept{} of the linear regression line
    divided by $2$. Here, $\mathtxt{ECS} = 3.14 \unit{K}$.}
  \label{fig:02:gregory_regression}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/gregory_regression_different_years.png}
  \caption{As in \cref{fig:02:gregory_regression} but for different time
    periods considered in the Gregory regression resulting in different values
    for the \acf{ECS} and the climate feedback parameter $\lambda$. Dark gray,
    blue, red and orange colors correspond to the \acf{CESM} of the \acf{NCAR}
    for different time periods of a long running simulation (see legend). The
    initial years are simulated many times for different initial conditions.
    Light gray colors correspond to the \acs{CMIP}5 ensemble (150 years each).
    \SpringerAdaptedFrom{Knutti2017}.}
  \label{fig:02:gregory_regression_different_years}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/tcr_calculation.pdf}
  \caption{Global and annual mean \acl{T} change $\Delta T$ for 140 years of a
    simulation with a $1 \unit{\%}$ per year increase of the atmospheric
    \acs{CO2} concentration (\onepctcotwo{}) for the \acf{CESM} of the
    \acf{NCAR} (blue circles). The temperature change is calculated relative
    to a corresponding pre-industrial control simulation smoothed with a
    linear fit over all 140 years. The \acf{TCR} is defined as the temperature
    change $\Delta T$ at the time of \acs{CO2} doubling averaged over a
    20-year period (illustrated by the vertical dashed lines). Here,
    $\mathtxt{TCR} = 2.35 \unit{K}$ (horizontal dashed line).}
  \label{fig:02:tcr}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/carbon_cycle_schematic.png}
  \caption{Simplified schematic of the global carbon cycle including the
    typical turnover time scales for carbon transfers through the major
    reservoirs (atmosphere, land surface and ocean).
    \IPCCReproducedFrom{Ciais2013}{their FAQ 6.2, figure 1}.}
  \label{fig:02:carbon_cycle_schematic}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/keeling_curve.pdf}
  \caption{The Keeling Curve: monthly mean atmospheric \acs{CO2} concentration
    at the Mauna Loa Observatory, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$; elevation: $3397 \unit{m}$) from 1958 to 2019
    \autocite{Keeling2005}. The steady increase of the atmospheric \acs{CO2}
    concentration is superimposed with a seasonal oscillation caused by the
    seasonal \acs{CO2} cycle (see \cref{subsec:02:carbon_cycle_overview}).}
  \label{fig:02:keeling_curve}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/carbon_cycle_perturbation.png}
  \caption{Schematic representation of the overall perturbation of the global
    carbon cycle caused by anthropogenic activities, averaged globally for the
    decade \range{2010}{2019}. Arrows represent carbon exchange fluxes; circles
    carbon reservoirs. More details are given in the legend of this figure.
    \AdaptedFrom{Friedlingstein2020}.}
  \label{fig:02:carbon_cycle_perturbation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/emergent_constraint.pdf}
  \caption{Schematic illustration of the emergent constraint approach. Basis of
    every emergent constraint is a robust and physically-interpretable emergent
    relationship (red line) between a target variable $y$ (\eg{} Earth system
    sensitivity or projection of future climate change) and an observable $x$
    (\eg{} past or present-day trend or variation) for the climate models of a
    multi-model ensemble (blue circles). With an observation of $x$,
    uncertainties in $y$ in the multi-model ensemble, illustrated by the yellow
    \acf{PDF}, can be reduced (gray \acs{PDF}). Uncertainties in the target
    variable $y$ arise from two sources: uncertainties in the observation (blue
    shaded area) and uncertainties in the emergent relationship (red shaded
    area). \SpringerAdaptedFrom{Eyring2019}.}
  \label{fig:02:emergent_constraint}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/mder_schematic.pdf}
  \caption{Schematic illustration of the \acf{MDER} approach
    \autocite{Karpechko2013}. First, inter-model relationships between a target
    variable $y$ and multiple process-based predictors $x^{(k)}$ (here: two
    predictors $x^{(1)}$ and $x^{(2)}$) are used to fit a multivariate linear
    regression model (gray surface). Second, observations of the predictors
    (horizontal black lines) are fed into the regression model to calculate an
    observation-based best estimate of the target variable $\hat{y}_0$
    following \cref{eq:02:mder_best_estimate}. The black circle indicates the
    best estimate for the target variable $y$ given by the observed values of
    $x^{(1)}$ and $x^{(2)}$. Each of the remaining colored circles represents
    a single climate model of the multi-model ensemble. The vertical dashed
    lines visualize the distance between the climate model data and the linear
    regression surface, which represents the noise term $\bm{\varepsilon}$ in
    \cref{eq:02:multivariate_linear_model}.}
  \label{fig:02:mder}
\end{figure}

>>>>

%=============================================================================%
%                            Doctoral Dissertation                            %
%                               Manuel Schlund                                %
%                                  (c) 2021                                   %
%=============================================================================%
%                            Scientific Background                            %
%=============================================================================%

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/esms_historical_evolution.pdf}
  \caption[
    Historical evolution of coupled climate models over the last 45 years.
  ]{
    Historical evolution of coupled climate models over the last 45 years. In
    early days, these models were so-called \acfp{AOGCM}, which only included
    three components: the atmosphere, the land surface and the ocean. Over the
    time, the individual components grew in complexity and included a wider
    range of processes (illustrated by the growing cylinders). Eventually, more
    and more components (aerosols, carbon cycle, \etc{}) were added to the
    coupled system, forming the modern \acfp{ESM}.
    \IPCCReproducedFrom{Cubasch2013}{their figure 1.13}.
  }
  \label{fig:02:esms_historical_evolution}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/cmip6.pdf}
  \caption[
    Schematic of the experiment design of Phase 6 of the \acl{CMIP}
    (\acs{CMIP}6).
  ]{
    Schematic of the experiment design of Phase 6 of the \acl{CMIP}
    (\acs{CMIP}6). The center of the circle illustrates the four \acs{DECK}
    (\acl{DECK}) experiments and the \acs{CMIP}6 historical simulation. The
    circular sectors show additional science themes that can be explored
    through the 21 \acs{CMIP}6-Endorsed \acfp{MIP}.
    \SpringerAdaptedFrom{Simpkins2017}.
  }
  \label{fig:02:cmip6}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/sources_of_uncertainty.pdf}
  \caption[
    Schematic illustrating the importance of different sources of
    uncertainties in climate model projections and their evolution in time.
  ]{
    Schematic illustrating the importance of different sources of
    uncertainties in climate model projections and their evolution in time. (a)
    Time series of the anomaly of the decadal and global mean surface
    temperature relative to the period \range{1961}{1980}. The black line
    shows the historical observations with estimates of uncertainty from
    climate models (gray). The remaining colors show different sources of
    uncertainty in future climate projections: Natural variability (orange),
    climate response uncertainty (blue) and emission uncertainty (green)
    \autocite{Hawkins2009, Hawkins2010}. Climate response uncertainty can
    increase (b) in newer generations of climate models when a new process is
    discovered to be relevant or decrease (c) with additional model
    improvements and observational constraints.
    \IPCCReproducedFrom{Cubasch2013}{their FAQ 1.1, figure 1}.
  }
  \label{fig:02:sources_of_uncertainty}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/feedbacks_overview.pdf}
  \caption[
    Climate feedbacks and corresponding time scales.
  ]{
    Climate feedbacks and corresponding time scales. \enquote{+} refers to
    positive feedbacks, which amplify the effect of the external forcing (\eg{}
    the water vapor feedback). \enquote{-} refers to negative feedbacks, which
    diminish the effect of the external forcing (\eg{} the longwave radiation
    feedback). \enquote{+/-} refers to feedbacks which might be either positive
    or negative (\eg{} the cloud feedback). The smaller box highlights the
    large differences in time scales for the various feedbacks.
    \IPCCReproducedFrom{Cubasch2013}{their figure 1.2}.
  }
  \label{fig:02:feedbacks_overview}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/gregory_regression.pdf}
  \caption[
    Gregory regression for the \acs{CMIP}5 \acl{MMM} illustrating the
    definition of the \acf{ECS}.
  ]{
    Global and annual mean net \acf{TOA} radiation $N$ versus the change in
    global and annual mean \acl{T} $\Delta T$ for 150 years of a simulation
    with an abrupt quadrupling of the atmospheric \acs{CO2} concentration
    (\nxcotwo{4}) for the \acs{CMIP}5 \acl{MMM} (blue circles). To account for
    energy leakage and model drift, a linear fit of the corresponding
    pre-industrial control run is subtracted from the \nxcotwo{4} simulation.
    As given by \cref{eq:02:N_vs_delta_t}, the slope of the linear regression
    (black line) corresponds to the climate feedback parameter $\lambda$, and
    the \yintercept{} corresponds to the radiative forcing $F_\mathtxt{4x}$.
    These can be used to calculate the \acf{ECS} with the Gregory regression
    method according to \cref{eq:02:ecs} \autocite{Gregory2004}. \acs{ECS} is
    equivalently given by the \xintercept{} of the linear regression line
    divided by $2$. Here, $\mathtxt{ECS} = 3.14 \unit{K}$.
  }
  \label{fig:02:gregory_regression}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/gregory_regression_different_years.png}
  \caption[
    Gregory regression for different time periods.
  ]{
    As in \cref{fig:02:gregory_regression} but for different time periods
    considered in the Gregory regression resulting in different values for the
    \acf{ECS} and the climate feedback parameter $\lambda$. Dark gray, blue,
    red and orange colors correspond to the \acf{CESM} of the \acf{NCAR} for
    different time periods of a long running simulation (see legend). The
    initial years are simulated many times for different initial conditions.
    Light gray colors correspond to the \acs{CMIP}5 ensemble (150 years each).
    \SpringerAdaptedFrom{Knutti2017}.
  }
  \label{fig:02:gregory_regression_different_years}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/tcr_calculation.pdf}
  \caption[
    Illustration of the definition of the \acf{TCR}.
  ]{
    Global and annual mean \acl{T} change $\Delta T$ for 140 years of a
    simulation with a $1 \unit{\%}$ per year increase of the atmospheric
    \acs{CO2} concentration (\onepctcotwo{}) for the \acf{CESM} of the
    \acf{NCAR} (blue circles). The temperature change is calculated relative to
    a corresponding pre-industrial control simulation smoothed with a linear
    fit over all 140 years. The \acf{TCR} is defined as the temperature change
    $\Delta T$ at the time of \acs{CO2} doubling averaged over a 20-year period
    (illustrated by the vertical dashed lines). Here, $\mathtxt{TCR} = 2.35
    \unit{K}$ (horizontal dashed line).
  }
  \label{fig:02:tcr}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/carbon_cycle_schematic.png}
  \caption[
    Simplified schematic of the global carbon cycle.
  ]{
    Simplified schematic of the global carbon cycle including the typical
    turnover time scales for carbon transfers through the major reservoirs
    (atmosphere, land surface and ocean). \IPCCReproducedFrom{Ciais2013}{their
      FAQ 6.2, figure 1}.
  }
  \label{fig:02:carbon_cycle_schematic}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/keeling_curve.pdf}
  \caption[
    The Keeling Curve.
  ]{
    The Keeling Curve: monthly mean atmospheric \acs{CO2} concentration at the
    Mauna Loa Observatory, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$; elevation: $3397 \unit{m}$) from 1958 to 2019
    \autocite{Keeling2005}. The steady increase of the atmospheric \acs{CO2}
    concentration is superimposed with a seasonal oscillation caused by the
    seasonal \acs{CO2} cycle (see \cref{subsec:02:carbon_cycle_overview}).
  }
  \label{fig:02:keeling_curve}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/carbon_cycle_perturbation.png}
  \caption[
    Schematic representation of the overall perturbation of the global carbon
    cycle caused by anthropogenic activities.
  ]{
    Schematic representation of the overall perturbation of the global carbon
    cycle caused by anthropogenic activities, averaged globally for the decade
    \range{2010}{2019}. Arrows represent carbon exchange fluxes; circles carbon
    reservoirs. More details are given in the legend of this figure.
    \AdaptedFrom{Friedlingstein2020}.
  }
  \label{fig:02:carbon_cycle_perturbation}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/emergent_constraint.pdf}
  \caption[
    Schematic illustration of the emergent constraint approach.
  ]{
    Schematic illustration of the emergent constraint approach. Basis of every
    emergent constraint is a robust and physically-interpretable emergent
    relationship (red line) between a target variable $y$ (\eg{} Earth system
    sensitivity or projection of future climate change) and an observable $x$
    (\eg{} past or present-day trend or variation) for the climate models of a
    multi-model ensemble (blue circles). With an observation of $x$,
    uncertainties in $y$ in the multi-model ensemble, illustrated by the yellow
    \acf{PDF}, can be reduced (gray \acs{PDF}). Uncertainties in the target
    variable $y$ arise from two sources: uncertainties in the observation (blue
    shaded area) and uncertainties in the emergent relationship (red shaded
    area). \SpringerAdaptedFrom{Eyring2019}.
  }
  \label{fig:02:emergent_constraint}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/mder_schematic.pdf}
  \caption[
    Schematic illustration of the \acf{MDER} approach.
  ]{
    Schematic illustration of the \acf{MDER} approach \autocite{Karpechko2013}.
    First, inter-model relationships between a target variable $y$ and multiple
    process-based predictors $x^{(k)}$ (here: two predictors $x^{(1)}$ and
    $x^{(2)}$) are used to fit a multivariate linear regression model (gray
    surface). Second, observations of the predictors (horizontal black lines)
    are fed into the regression model to calculate an observation-based best
    estimate of the target variable $\hat{y}_0$ following
    \cref{eq:02:mder_best_estimate}. The black circle indicates the best
    estimate for the target variable $y$ given by the observed values of
    $x^{(1)}$ and $x^{(2)}$. Each of the remaining colored circles represents a
    single climate model of the multi-model ensemble. The vertical dashed lines
    visualize the distance between the climate model data and the linear
    regression surface, which represents the noise term $\bm{\varepsilon}$ in
    \cref{eq:02:multivariate_linear_model}.
  }
  \label{fig:02:mder}
\end{figure}
